---
title: "Code chunk options"
author: "Anonymous"
date: "August 7th, 2022"
output: 
  html_document:
    toc: true
    number_sections: true
---

```{r Rmd-init, include = FALSE}
## The code in this chunk will be executed, will not appear in rendered .html file

##  Silently sets knitr chunk options used in Rmd file
require(knitr)
knitr::opts_chunk$set(
  collapse = TRUE,
  results = "markup",  
  comment="#>",
  highlight = TRUE,
  fig.width = 12, fig.height=8, fig.path='Figs/'
)


# Silently clears Global environment
rm(list=ls())

.params <- list(vignette_nm = "95-test-chunks") # !!!

# Silently assign variables for later use
vignette_nm  <- .params$vignette_nm   # .params refers to list defined above
vignette_Rmd <- paste(vignette_nm,".Rmd", sep = "")
vignette_R   <- paste(vignette_nm,".R",   sep = "")
vignette_html<- paste(vignette_nm, ".html",   sep = "")
```

Options used in the yaml header are described in more detail
[here](https://bookdown.org/yihui/rmarkdown/documents.html).

# Main section

The `r vignette_Rmd` document provides examples of code chunk options.

* Executed by: `r Sys.getenv("USERNAME")` on `r Sys.time()`.  
* Located in `r getwd()` folder. 
* Used to generate `r vignette_html` and `r vignette_R` documents
* Options used in the yaml header are described in more detail
[here](https://bookdown.org/yihui/rmarkdown/documents.html).

## Examples of code chunk options


### Default code chunk options

* By default knitr will run the code chunk and will display output as shown below.
* Lines of the output are preceeded with `#>" will appear in the finished (e.g. html) file.  
* Lines with R code will appear in `r vignette_R` file

```{r sessionInfo}
ls()
vignette_nm
sessionInfo()
```

### Option include = FALSE

This example illustrates how the code chunk in this example reads: 

```
(test_include <- "Test include") # example code displayed for reference only  
```

This code chunk (not shown) was executed  using combination of two options:  `echo=FALSE, results="hide"`.


* option `include = FALSE` prevents code and results from appearing in the finished (e.g html) file.
* R Markdown runs the code in the chunk, and the results can be used by subsequent chunks
* R statements are _saved_ in `r vignette_R` file and are ready for execution


```{r test-include2, include = FALSE}
# Note: This code/results are not displayed in rendered html file 
(test_include2 <- "Test include: include = FALSE")
```

The following code/output confirms that the code chunk was indeed executed.

```{r test-include2-check}
exists("test_include2")
test_include2
```


### Commenting out code chunks in tangle .R file

* echo =FALSE: Corresponding code change does not show in the html file 

```{r test-tangle-out, echo= FALSE, eval=FALSE, comment = "##"}
(test_tangle <- "Test tangle")
```
The following output confirms that code chunk was not executed (as intended)

```{r test-tangleout-check}
exists("test_tangle")
```

## Figure example

```{r test-figure, echo = FALSE, fig.height=4, fig.width=8, dev ="svg"}
plot(cars)
```

Save results in external Rdata file(s) for later use.

```
save(test_knitr_setup,test_include, "Rdata/90-test-chunks.Rdata")
```


